Simulating the Linux page cache in distributed applications with the WRENCH library

### 2020-12-08 paper_io_sim.tex
edits in results

        Figure~\ref{fig:single_error} shows the relative error of simulated
        read and write times throughout the three application tasks. The
        page cache simulation model drastically reduces simulation errors
        for all I/O operations except the first read that deals with
        uncached data. Errors are reduced from an average of \texttt{xxx\%}
        in WRENCH to \texttt{yyy \%} in the Python prototype and
        \texttt{zzz \%} in WRENCH-cache. The original WRENCH simulator significantly overestimates
        read and write times, due to its lack of page cache simulation
        model.

>>>>

        Figure~\ref{fig:single_error} shows the relative error of simulated
        read and write times throughout the three application tasks. The
        page cache simulation model drastically reduces simulation errors
        for all I/O operations except the first read as it only involves
        uncached data. Errors are reduced from an average of \texttt{xxx\%}
        in WRENCH to \texttt{yyy \%} in the Python prototype and
        \texttt{zzz \%} in WRENCH-cache \tristan{Dzung, update average percentages}.
        Unsurprisingly, the original WRENCH simulator significantly overestimates
        read and write times, due to its lack of page cache simulation
        model.
